On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence

### 2017-09-18 Thesis/20170916_Draft.Rmd
Printed version

Consider the problem the latter companies face. Whenever a user reports that she visited a restaurant, the app would like to ask questions about her experience. To give a simple example, assume users are not willing to answer more than one question per restaurant visit, and the app would like to find out two things: Does the restaurant have good service? Is the restaurant trendy?

@@

This is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006, or \autoref{theorem:ChernoffStein}), in which the optimal error exponent is based on the Kullback-Leibler divergence. We arrive at this result as the one-armed bandit does not require sequential sampling: The single arm receives all samples. $\mathbb{E}_{\nu'}[N_1(t)]$ is not a random variable but equals $T$. The single-armed bandit is a simple hypothesis test.

@@

$$
- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
$$
\end{corollary}\label{corollary:LBKTBP}

We present the proofs of \autoref{sec:LBTBP} in the appendix in \autoref{sec:corollaryLBTBPproof}. Corresponding to the complexity measures defined in equation $(1)$ of Kaufmann et al. (2016), we can define the complexity $\kappa_{TBP}(\nu)$ in the thresholding bandit problem and lower bound it:

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR"), 
                   each = 1991), rep("B-UCB", 3991), rep("EVT", 1981))
index <- c(rep(10:2000, times = 4), 10:4000, 20:2000)
alg_res <- log(c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
                 loc2_comp_AugUCB_2000, loc2_comp_LR_2000,
                 loc2_comp_BUCB_horizon_4000, loc2_comp_EVT))
loc2_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc2_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = names, color = names)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(subtitle = "Dashed Line indicates Error = 0.1.",
       y = "log(Error)", x = "Round Index") + 
  coord_cartesian(xlim = c(0,2000)) +
  scale_color_discrete(name = "Algorithm") + 
  theme_bw() #+
  #theme(legend.position = "bottom")

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB",
                     "SLR", "SLR-D", "B-UCB"), 
                   each = 6991), rep("EVT", 6981))
index <- c(rep(10:7000, times = 6), 20:7000)
alg_res <- log(c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
                 loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
                 loc6nt_comp_LRD,
                 loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
loc6nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", 
                     "SLR", "SLR-D", "B-UCB"), 
                   each = 9990), rep("EVT", times = 9979))
index <- c(rep(11:10000, times = 6), 22:10000)
alg_res <- log(c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
                 loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
                 loc7nt_comp_LRD_10000,
                 loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
loc7nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

ggplot(sim23_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  facet_grid(.~Simulation, scales = "free") +
  labs(subtitle = "Dashed Line indicates Error = 0.1.",
       y = "log(Error)", x = "Round Index") +
  scale_color_discrete(name = "Algorithm") +
  theme_bw() + 
  theme(legend.position = "bottom")
```

```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '70%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
library(dplyr)

@@

alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
                   each = 3981), rep("EVT", 3961))
index <- c(rep(20:4000, times = 4), 40:4000)
alg_res <- log(c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
                 exp2_comp_AugUCB, exp2_comp_EVT))
exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(exp2_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(subtitle = "Dashed Line indicates Error = 0.1.",
       y = "log(Error)", x = "Round Index") +
  theme_bw()# +
  #theme(legend.position = "bottom")
```

@@

alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
                   each = 3981), rep("EVT", 3961))
index <- c(rep(20:4000, times = 4), 40:4000)
alg_res <- log(c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
                 exp2_comp_AugUCB, exp2_comp_EVT))
exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

alg_names <- c(rep(c("Uniform", "APT", "SLR", "AugUCB"), each = 9981), 
               rep("EVT", 9961))
index <- c(rep(20:10000, times = 4), 40:10000)
alg_res <- log(c(pois2_comp_UNIFORM, pois2_comp_APT, 
                 pois2_comp_LR, pois2_comp_AugUCB, pois2_comp_EVT))
pois2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

ggplot(exp45_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  facet_grid(.~Distribution, scales = "free") +
  labs(#title = "Results of Experiment 5", 
       subtitle = "Dashed line at Error = 0.1.", 
       y = "log(Error)", x = "Round Index") +
  theme_bw() +
  theme(legend.position = "bottom")
```

@@

In the following, we present the results of two experiments performed on a real world data set. While most multi-armed bandit algorithms are assessed on synthetic data, as we have done in \autoref{sec:SyntheticData}, a real world data set is useful to observe how algorithms perform in presence of, for example, not perfectly i.i.d. samples. Every company of course tries to run their algorithms under settings as ideal as possible, but there will always be problems. Thus our experiments serve as a first robustness check on the algorithms introduced before.

@@

Data have been collected by the German online shop [Amorelie](https://amorelie.de) as part of standard website analytics. For 197 selected products, we observe the number of users visiting each product's detail page (PDP) during a given minute. The data set we use here has been collected during the entire month of November 2016. It can be considered time series data collected at minutely frequency. Thus the data contain 43200 observations per product, and overall 8510400 observations.

Since we want to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm. Given that, it is easy to evaluate the perfomance of algorithms that make different decisions at different point in times and thus do not observe the same samples. By having an observation for each arm at any given time point, each algorithm had at least the opportunity to observe a certain sample. Other papers (for example, Li et al., 2011) have solved this problem by using a sample drawn uniformly during, for example, an A/B test. Then, if the next observation in the sample is not from the same arm that the algorithm would like to draw from, observations are discarded until the next observation from the selected arm.

The choice of using what is basically multiple time series data as the sample offers a simple way of running the algorithms just as often on the data as for simulated data. The goal is to perform 5000 runs over the sample to confidently assess the performance. Since we would like to preserve potential time dependencies in the data, a simple resampling of the data is not an option to create the needed 5000 variations of the sample. Instead we perform time series cross validation. To preserve the autocorrelation, one can create different samples of $X$ observations by sliding a window of size $X$ over the time series. Moving the window one period (in our case one minute) at a time, one ensures that no sample shares start and end observation with another sample. In particular, this means for a given bandit strategy and two samples that the observations that the algorithm collects as feedback during the initialization phases differ from sample to sample and are never the same. This is because during initialization every strategy pulls arms $1, ..., K$ (or $1,...,2K$ for EVT) once in this order.

@@

While the data set consists of count data (the number of visits to a PDP during a given minute), we binarize the data by applying a certain threshold. If the count is above this threshold, the new observation is $1$, else $0$. Thus we have a binary time series of length $60\cdot 24 \cdot 30 = 43200$ for each of the 197 products. Given that the number of visitors that reach a given PDP is likely to vary by time of day and by day, and in general over time, we expect the mean of the time series to not be stable over time. For example, less visitors visit during night than during the evening. This leads to a decrease in the average number of visits, and creates a daily seasonality. On the other hand, more users may visit the site during a weekend, thus leading to a spike on Saturdays and Sundays. Because of the latter time dependency, it is best practice to run online A/B tests for at least a week^[See for example the "A/B Testing in the Wild" presentation by Emily Robinson, <https://youtu.be/SF-ryGgLOgQ>], or an integer multiple of weeks, so as to take into account the weekly seasonality in the time series. For this reason, the experiments we present below are run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR","B-UCB"), 
                   each = 10071), rep("EVT", 10061))
index <- c(rep(10:10080, times = 5), 20:10080)
alg_res <- log(c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
loc3_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(loc3_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(#title = "Results of Real Data Experiment 1", 
       subtitle = paste0("Dashed Line indicates Error = 0.1."), 
       y = "log(Error)", x = "Round Index") +
  theme_bw()
```

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "B-UCB"), 
                   each = 10071), rep("EVT", 10061))
index <- c(rep(10:10080, times = 5), 20:10080)
alg_res <- log(c(amo4_comp_UNIFORM, amo4_comp_APT, amo4_comp_AugUCB, amo4_comp_LR, amo4_comp_BUCB, amo4_comp_EVT))
source_name <- rep("Real", 60416)
loc4_comp_res <- data.frame(source = source_name, 
                            index = index, names = alg_names, 
                            results = alg_res)

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "SLR", "B-UCB"), 
                   each = 10071), rep("EVT", 10061))
index <- c(rep(10:10080, times = 5), 20:10080)
alg_res <- log(c(amo4sim_comp_UNIFORM, amo4sim_comp_APT, amo4sim_comp_AugUCB,
                 amo4sim_comp_LR, amo4sim_comp_BUCB, amo4sim_comp_EVT))
source_name <- rep("Synthetic", 60416)
loc4sim_comp_res <- data.frame(source = source_name, index = index, 
                               names = alg_names, results = alg_res)
loc4total <- rbind(loc4_comp_res, loc4sim_comp_res) %>%
  rename(Algorithm = names)

ggplot(loc4total, aes(x = index, y = results, 
                      group = Algorithm, color = Algorithm)) + 
  geom_line() +
  facet_grid(.~source) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(#title = "Results of Real Data Experiment 2", 
       subtitle = paste0("Dashed line indicates Error = 0.1."), 
       y = "log(Error)", x = "Round Index") +
  theme_bw() +
  theme(legend.position = "bottom")
```

@@

@@

@@

## Empirical Analysis of the Bayes-UCB Algorithm in Simulation 2

@@

## Empirical Comparison of APT, SLR, and Bayes-UCB in Simulation 2

>>>>

Consider the problem the latter companies face. Whenever a user reports that she visited a restaurant, the app would like to ask questions about her experience. To give a simple example, assume users are not willing to answer more than one question per restaurant visit, and the app would like to find out two things: Does the restaurant have good service? Is the restaurant trendy? See \autoref{sec:Foursquare} for what this information looks like in the Foursquare app.

@@

This is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006, or \autoref{theorem:ChernoffStein}), in which the optimal error exponent is based on the Kullback-Leibler divergence. We arrive at this result as the one-armed bandit does not require sequential sampling: The single arm receives all samples. $\mathbb{E}_{\nu'}[N_1(t)]$ is not a random variable but equals $T$. The single-armed bandit is a simple hypothesis test on a sample of size $T$. In a way, it is a degenerate case of a multi-armed bandit problem.

We present the proofs of \autoref{sec:LBTBP} in the appendix in \autoref{sec:corollaryLBTBPproof}. While we were hoping to also prove a lower bound for the $K$-armed bandit problem, we were not able to do so as this entails the expectation under the alternative problem of the number of times the changed arm $a$ is pulled. Compare to the proof for the two-armed pure exploration bandit in Kaufmann et al. (2016).

@@

$$
- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
$$
\end{corollary} Corresponding to the complexity measures defined in equation $(1)$ of Kaufmann et al. (2016), we can define the complexity $\kappa_{TBP}(\nu)$ in the thresholding bandit problem and lower bound it:

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR"), 
                   each = 1991), rep("B-UCB", 3991), rep("EVT", 1981))
index <- c(rep(10:2000, times = 4), 10:4000, 20:2000)
alg_res <- (c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
                 loc2_comp_AugUCB_2000, loc2_comp_LR_2000,
                 loc2_comp_BUCB_horizon_4000, loc2_comp_EVT))
loc2_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc2_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = names, color = names)) +
  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
       y = "Error (log10 scale)", x = "Round Index") + 
  coord_cartesian(xlim = c(0,2000)) +
  scale_color_discrete(name = "Algorithm") + 
  theme_bw() +
  scale_y_log10() #+
  #theme(legend.position = "bottom")

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB",
                     "SLR", "SLR-D", "B-UCB"), 
                   each = 6991), rep("EVT", 6981))
index <- c(rep(10:7000, times = 6), 20:7000)
alg_res <- (c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
                 loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
                 loc6nt_comp_LRD,
                 loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
loc6nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", 
                     "SLR", "SLR-D", "B-UCB"), 
                   each = 9990), rep("EVT", times = 9979))
index <- c(rep(11:10000, times = 6), 22:10000)
alg_res <- (c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
                 loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
                 loc7nt_comp_LRD_10000,
                 loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
loc7nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

ggplot(sim23_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  #geom_hline(aes(yintercept = (0.1)), linetype = 2) +
  facet_grid(.~Simulation, scales = "free") +
  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
       y = "Error (log10 scale)", x = "Round Index") +
  scale_color_discrete(name = "Algorithm") +
  theme_bw() + 
  theme(legend.position = "bottom") +
  scale_y_log10()
```

```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
library(dplyr)

@@

alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
                   each = 3981), rep("EVT", 3961))
index <- c(rep(20:4000, times = 4), 40:4000)
alg_res <- (c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
                 exp2_comp_AugUCB, exp2_comp_EVT))
exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(exp2_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
       y = "log(Error)", x = "Round Index") +
  theme_bw() +
  scale_y_log10()# +
  #theme(legend.position = "bottom")
```

@@

alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
                   each = 3981), rep("EVT", 3961))
index <- c(rep(20:4000, times = 4), 40:4000)
alg_res <- (c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
                 exp2_comp_AugUCB, exp2_comp_EVT))
exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

alg_names <- c(rep(c("Uniform", "APT", "SLR", "AugUCB"), each = 9981), 
               rep("EVT", 9961))
index <- c(rep(20:10000, times = 4), 40:10000)
alg_res <- (c(pois2_comp_UNIFORM, pois2_comp_APT, 
                 pois2_comp_LR, pois2_comp_AugUCB, pois2_comp_EVT))
pois2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)

@@

ggplot(exp45_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  facet_grid(.~Distribution, scales = "free") +
  labs(#title = "Results of Experiment 5", 
       #subtitle = "Dashed line at Error = 0.1.", 
       y = "Error (log10 scale)", x = "Round Index") +
  theme_bw() +
  theme(legend.position = "bottom") +
  scale_y_log10()
```

@@

In the following, we present the results of two experiments performed on a real world data set. While most multi-armed bandit algorithms are assessed on synthetic data, as we have done in \autoref{sec:SyntheticData}, a real world data set is useful to observe how algorithms perform in presence of, for example, not perfectly i.i.d. samples. Every experimenter of course tries to run their algorithms under settings as ideal as possible, but there will always be problems. Thus our experiments serve as a first robustness check on the algorithms introduced before.

@@

Data have been collected by the German online shop [Amorelie](https://amorelie.de) as part of standard website analytics. For 197 selected products, we observe the number of users visiting each product's detail page (PDP) during a given minute. The data set we use here has been collected during the entire month of November 2016. It can be considered time series data sampled at minutely frequency. Thus the data contain 43200 observations per product, and in total 8510400 observations.

Since we would like to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm. Given that, it is easy to evaluate the perfomance of algorithms that make different decisions at different point in times and thus do not observe the same samples. By having an observation for each arm at any given time point, each algorithm had at least the opportunity to observe a certain sample. Other papers (for example, Li et al., 2011) have solved this problem by using a sample drawn uniformly during, for example, an A/B test. Then, if the next observation in the sample is not from the same arm that the algorithm would like to draw from, observations are discarded until the next observation from the selected arm.

The choice of using what is essentially multivariate time series data as the sample offers a simple way of running the algorithms just as often on the real data as on simulated data. The goal is to perform 5000 runs over the sample to confidently assess the performance. Since we would like to preserve potential time dependencies in the data, a simple resampling of the data is not an option to create the needed 5000 variations of the sample. Instead we perform time series cross validation. To preserve the autocorrelation, one can create different samples of $n$ observations by sliding a window of size $n$ over the time series. Moving the window one period (in our case one minute) at a time, one ensures that no sample shares start and end observation with another sample (see Figure 8)^[The graphic is adapted from a graphic by Rob J. Hyndman available at <https://gist.github.com/robjhyndman/9fa152c585442bb076eb42a30a020091>]. In particular, this means for a given bandit strategy and two samples that the observations that the algorithm collects as feedback during the initialization phases differ from sample to sample and are never the same. This is because during initialization every strategy pulls arms $1, ..., K$ (or $1,...,2K$ for EVT) once in this order.

```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "We use time series crossvalidation, to create many samples from one data set."}
plot(0,0,xlim=c(0,28),ylim=c(0,1),
     xaxt="n",yaxt="n",bty="n",xlab="",ylab="",type="n")
i <- 1
for(j in 1:20)
{
  test <- (6+j):26
  train <- 1:(5+j)
  pre_train <- 1:(j-1)
  arrows(0,1-j/20,27,1-j/20,0.05)
  points(train,rep(1-j/20,length(train)),pch=19,col="blue")
  if(j > 1)
    points(pre_train, rep(1-j/20,length(pre_train)),pch=19,col="gray")
  if(length(test) >= i)
    points(test[i], 1-j/20, pch=19, col="red")
  if(length(test) >= i)
    points(test[-i], rep(1-j/20,length(test)-1), pch=19, col="gray")
  else
    points(test, rep(1-j/20,length(test)), pch=19, col="gray")
}
text(28,.95,"time")
```

While the data set consists of count data (the number of visits to a PDP during a given minute), we binarize the data by applying a certain threshold. If the count is above this threshold, the new observation is $1$, else $0$. Thus we have a binary time series of length $60\cdot 24 \cdot 30 = 43200$ for each of the 197 products. Given that the number of visitors that reach a given PDP is likely to vary by time of day, by day, and in general over time, we expect the mean of the time series to not be stable over time. For example, less visitors visit during night than during the evening. This leads to a decrease in the average number of visits, and creates a daily seasonality. On the other hand, more users may visit the site during a weekend, thus leading to a spike on Saturdays and Sundays. Because of the latter time dependency, it is best practice to run online A/B tests for at least a week^[See for example the "A/B Testing in the Wild" presentation by Emily Robinson, <https://youtu.be/SF-ryGgLOgQ>], or an integer multiple of weeks, so as to take into account the weekly seasonality in the time series. For this reason, the experiments we present below are run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.

@@

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR","B-UCB"), 
                   each = 10071), rep("EVT", 10061))
index <- c(rep(10:10080, times = 5), 20:10080)
alg_res <- (c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
loc3_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(loc3_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = Algorithm, color = Algorithm)) +
  geom_hline(aes(yintercept = (0.1)), linetype = 2, color = "lightgrey") +
  labs(#title = "Results of Real Data Experiment 1", 
       #subtitle = paste0("Dashed Line indicates Error = 0.1."), 
       y = "Error (log10 scale)", x = "Round Index") +
  theme_bw() +
  scale_y_log10()
```

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "B-UCB"), 
                   each = 10071), rep("EVT", 10061))
index <- c(rep(10:10080, times = 5), 20:10080)
alg_res <- (c(amo4_comp_UNIFORM, amo4_comp_APT, amo4_comp_AugUCB, amo4_comp_LR, amo4_comp_BUCB, amo4_comp_EVT))
source_name <- rep("Real", 60416)
loc4_comp_res <- data.frame(source = source_name, 
                            index = index, names = alg_names, 
                            results = alg_res)

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "SLR", "B-UCB"), 
                   each = 10071), rep("EVT", 10061))
index <- c(rep(10:10080, times = 5), 20:10080)
alg_res <- (c(amo4sim_comp_UNIFORM, amo4sim_comp_APT, 
                 amo4sim_comp_AugUCB,
                 amo4sim_comp_LR, amo4sim_comp_BUCB, amo4sim_comp_EVT))
source_name <- rep("Synthetic", 60416)
loc4sim_comp_res <- data.frame(source = source_name, index = index, 
                               names = alg_names, results = alg_res)
loc4total <- rbind(loc4_comp_res, loc4sim_comp_res) %>%
  rename(Algorithm = names)

ggplot(loc4total, aes(x = index, y = results, 
                      group = Algorithm, color = Algorithm)) + 
  geom_line() +
  facet_grid(.~source) +
  #geom_hline(aes(yintercept = (0.1)), linetype = 2) +
  labs(#title = "Results of Real Data Experiment 2", 
       #subtitle = paste0("Dashed line indicates Error = 0.1."), 
       y = "Error (log10 scale)", x = "Round Index") +
  theme_bw() +
  theme(legend.position = "bottom") +
  scale_y_log10()
```

@@

In the thesis at hand, we have introduced the general thresholding bandit problem introduced by Locatelli et al. (2016), as well as their Anytime Parameter-Free Thresholding algorithm that tries to solve the problem optimally. Given a few limitations of the APT algorithm, we explored the literature on top-$m$ multi-armed bandit problems to see how the Kullback-Leibler divergence can be used to improve algorithms and performance bounds. Based on this we exhibit the similarity between the thresholding bandit problem and simple hypothesis testing. We derive a lower bound on the complexity of a one-armed thresholding bandit that corresponds to the Chernoff-Stein Lemma. Continuing with the intuition from hypothesis testing, we propose the new Simple Likelihood Ratio algorithm for the multi-armed thresholding bandit for one-parameter exponential family of distributions. We show in extensive simulations that the the empirical performance of the SLR algorithm improves significantly upon the APT algorithm. We show that adding the D-Tracking Rule originally proposed by Garivier and Kaufmann (2016) can eradicate some of the remaining weaknesses. We propose a new method of testing thresholding bandit algorithms on real data by treating it as in time series cross validation. We show that the adaptive sampling strategies are not robust to the time dependency in the data set.

Problems for future work are the derivation of lower and upper bounds on the error probability of the SLR algorithm. Furthermore, one might be able to adapt the lower bound on the complexity of the one-armed thresholding bandit to the multi-armed version. Lastly, the surprisingly very good performance of the Bayes-UCB algorithm in our simulations, as well as its better sample allocation to individual arms in terms of concentration compared to APT and SLR, justify more research effort, and a theoretical analysis of its performance.

@@

## Example of User Feedback in Foursquare App \label{sec:Foursquare}

![The right screenshot shows aggregated user feedback in the Foursquare app. One could use thresholding bandit algorithms as presented in this thesis to ask different questions so as to optimize the confidence with which the results are displayed for a restaurant in the app.](figures/Foursquare_Screenshot.png)

@@

### Empirical Analysis of the Bayes-UCB Algorithm in Simulation 2

@@

### Empirical Comparison of APT, SLR, and Bayes-UCB in Simulation 2
